---
title: A Test on Displaying R Plots on Pelican
date: 2018-04-21
category: misc
author: John Cabiles
runtime: shiny
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

I'm not entirely sure how markdown files containing R code will look on this Pelican website.  To make sure that plots I generate will actually show up, I've created a really simply plot on this R markdown file.  Then I'll see if the plot will be successfully displayed on the webpage.

Let's cross our fingers.

## Sample Data

The code below is from the R Markdown Cheat Sheet, which can be found on [the R Markdown cheat sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf).

I also used sample code from [Frank McCown](https://www.harding.edu/fmccown/r/).

```{r echo = TRUE}

# Define 2 vectors
cars <- c(1, 3, 6, 4, 9)
trucks <- c(2, 5, 4, 5, 12)

# Graph cars using a y axis that ranges from 0 to 12
plot(cars, type="o", col="blue", ylim=c(0,12))

# Graph trucks with red dashed line and square points
lines(trucks, type="o", pch=22, lty=2, col="red")

# Create a title with a red, bold/italic font
title(main="Autos", col.main="red", font.main=4)

```
